{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-07-31 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes, late night

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}

@@

>>>>

\begin{abstract} 
    Reports on papers read. 
    This is a LaTEX file for my own notes taking. 
    It may accelerate the process of writing my thesis for my PhD degree. 
    \todoinline{This paper is currently in draft mode. Check source to change options. }
\end{abstract}

@@

\chapter{Going deeper into the literatures}
    This chapter follows the previous chapter but delve deeper into the specifics of the literatures. 
    Most of the thing written here are my own thoughts and inspirations instead of translated ideas from the existing literatures. 
    \section{Quasi strong convexity is a wasteful definition}

### 2025-07-31 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes, late night

                    z \mapsto \partial g(x) + \langle \nabla f(x), z - x\rangle + 

@@

            Fix any $x \in \RR^n$ there exists a $B \ge 0$,  $\tilde x$ be an estimate of $T_B(x | F)$ such that $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 

@@

            &= \expect \left\Vert \nabla f(x) - \expect \tilde \nabla f(x) \right\Vert^2 

@@

            Suppose that that $\Phi_k, \lambda_k, R_k$ are as given in Theorem \ref{thm:snag-generic-cnvg}. 

>>>>

                    z \mapsto \partial g(z) + \langle \nabla f(x), z - x\rangle + 

@@

            Let $x \in \RR^n$, and let $\tilde x$ be an estimate of $T_B(x | F)$ such that $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, where $B \ge 0$. 

@@

            &= \expect \left\Vert \expect \tilde \nabla f(x) - \tilde \nabla f(x) \right\Vert^2 

@@

            Suppose that $\Phi_k, \lambda_k, R_k$ are as given in Theorem \ref{thm:snag-generic-cnvg}. 
